---
title: "AirPassengers Transformation"
author: "Edimilson Torres de Oliveira Neto"
date: "2023-10-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Importing the function from the R file of the repository
source("data_transformation.R")
```

## Air Passengers Transformation

The Air Passengers Dataset is a built-in R dataset that contains, Monthly totals of international airline passengers, from 1949 to 1960, measured in thousands.

The Air Passengers data is originally provided in a Time Series format.

```{r AirPassengers_Original}
AirPassengers
```
The data_transform function available on the "data_transformation.R" transforms this dataset into a tidy Data Frame with the columns Year, Month and Passengers

```{r AirPassengers_Transformation}
#Assigning the data to a variable
data <- AirPassengers

#Using the function
data <- data_transform(data)

#Printing the transformed data
print(head(data))

```
The data_transform function has two arguments "data" and "by_year". The first one should provides the "AirPassengers" original dataset. The second parameter is optional and it has a default value of FALSE. In case the parameter is changed to TRUE, the resulting dataset will be presented grouped by Year.

```{r AirPassengers_by_year}
#Assigning the original AirPassengers to the dataset
data_by_year <- AirPassengers

#Printing the transformed data grouped by year
data_by_year <- data_transform(data_by_year, by_year = TRUE)

#Printing the result
print(head(data_by_year))

```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
# this chunk generates the complete code appendix. 
# eval=FALSE tells R not to run (``evaluate'') the code here (it was already run before).
```